NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-03-06 Manuscript/manuscriptPS.tex
Updates related to issues https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/42 , https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/43 and https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/34

\caption{The list of MD simulations of pure PS bilayers without additional salt along with the references to the force fields used and the MD trajectories. Notation 2$\times$[time] indicates that more than two independent MD runs was conducted. Additional simulation details are given in the supplementary information.

@@

  reported in the experiments by Roux et al.~\cite{roux90}.  Notation 2$\times$[time] indicates that more than two independent MD runs was conducted. The simulation details are given in the supplementary information. 

@@

lipid/counter-ions  & force field for lipids / ions  & {[}CaCl$_{2}${]}\,(M)  & \footnote{Number of lipid molecules with largest mole fraction}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Number of additional cations}N$_{{\rm c}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120 & 5760  & 0  & 298  & 400 \todoi{lenght wrong? Check zenodo} & 250 \todoi{lenght wrong? Check zenodo} &  \todoi{this ref is to trajectory with CA}\cite{POPCpopsMACROG}\tabularnewline

@@

\begin{figure}[!tb]
  \centering
  \includegraphics[width=8.5cm]{../Figs/fig1_POPS.pdf}
  \caption{\label{PShgSIGNSsimpson}
    The headgroup and glycerol backbone region of the (A) INEPT spectrum and
    (B) 2D R-PDLF spectra.
    (C) Experimental S-DROSS data (points), and SIMPSON simulations (blue lines) with
    the C--H bond order parameter values of -0.12 for the $\beta$-carbon, and +0.09 and -0.02
    for the $\alpha$-carbon.
    Dashed gray line is the S-DROSS curve from a SIMPSON simulation with a positive value (+0.02) 
    for the smaller $\alpha$-carbon C--H bond order parameter.
  }
  \todo{I think that the peak labeling would be good to show also in (A).}\\
%  \todo{Also for $\alpha$ these are OPs, right,  thus we could just exclude the word 'splittings'?}
%  \todo{Please confirm: Was the positive value used for $\alpha$ in the gray curve 0.02?}
\end{figure}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PCPScomp.eps}
  \caption{\label{HGorderParameters}
    (A) Chemical structures and labels for the headgroup and glycerol backbone carbons.
    (B) Headgroup and glycerol backbone order parameters of POPS (T = 298 K) measured in this work compared
    with the previously published values from DOPS (T = 303 K, $^2$H NMR, 0.1M of NaCl) \cite{browning80} and 
    POPC  (T = 300 K, $^{13}$C NMR) \cite{ferreira13} experiments. Signs of the PS order parameters
    are measured in this work whereas signs of the PC order parameters are measured previously~\cite{ferreira16}.
  }\todo{
  1) Use diamonds for DOPS, spheres for POPS.
  2) Error bars?
  3) Change the y-label to $S_\mathrm{CH}$, and invert the y-axis, as in Fig. 3.
  4) Make lower g1 POPC visible, e.g., by slightly larger point.
  }
\end{figure}

>>>>

\caption{The list of MD simulations of pure PS bilayers without additional salt along with the references to the force fields used and the MD trajectories.
  Notation 2$\times$[time] indicates that two independent MD runs was conducted. Additional simulation details are given in the supplementary information.

@@

  reported in the experiments by Roux et al.~\cite{roux90}.  Notation 2$\times$[time] indicates that two independent MD runs was conducted.
  The simulation details are given in the supplementary information. 

@@

lipid/counter-ions  & force field for lipids / ions  & {[}CaCl$_{2}${]}\,(M)  & \footnote{Number of POPC molecules}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Number of additional cations}N$_{{\rm c}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120 & 5760  & 0  & 298  & 400 & 250 &  \cite{POPCpopsMACROG}\tabularnewline

@@

\begin{figure}[!tb]
  \centering
  \includegraphics[width=8.5cm]{../Figs/fig1_POPS.pdf}
  \caption{\label{PShgSIGNSsimpson}
    The headgroup and glycerol backbone region of the (A) INEPT spectrum and
    (B) 2D R-PDLF spectra.
    (C) Experimental S-DROSS data (points), and SIMPSON simulations (blue lines) with
    the C--H bond order parameter values of -0.12 for the $\beta$-carbon, and +0.09 and -0.02
    for the $\alpha$-carbon.
    Dashed gray line is the S-DROSS curve from a SIMPSON simulation with a positive value (+0.02) 
    for the smaller $\alpha$-carbon C--H bond order parameter.
  }
  \todo{I think that the peak labeling would be good to show also in (A).}\\
%  \todo{Also for $\alpha$ these are OPs, right,  thus we could just exclude the word 'splittings'?}
%  \todo{Please confirm: Was the positive value used for $\alpha$ in the gray curve 0.02?}
\end{figure}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PCPScomp.eps}
  \caption{\label{HGorderParameters}
    (A) Chemical structures and labels for the headgroup and glycerol backbone carbons.
    (B) Headgroup and glycerol backbone order parameters of POPS (T = 298 K) measured in this work compared
    with the previously published values from DOPS (T = 303 K, $^2$H NMR, 0.1M of NaCl) \cite{browning80} and 
    POPC  (T = 300 K, $^{13}$C NMR) \cite{ferreira13} experiments. Signs of the PS order parameters
    are measured in this work whereas signs of the PC order parameters are measured previously~\cite{ferreira16}.
    The size of errorbars ($\pm$0.02) shown for $^{13}$C NMR data is justified previously~\cite{botan15,ollila16}. 
  }
  \todo{Replacing the "literature" with "from Ref X" has been suggested  https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/34.
  We can do this just before submission when citation numbers will not change anymore.}
\end{figure}
